Computer Science House Constitution

### 2022-02-14 constitution.tex
constitution: reorder waivable requirements for consistency

\asubsection{Overriding Directorships Qualifications}
When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in \ref{Qualifications}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.

>>>>

\asubsection{Waiving of Requirements}
\begin{enumerate}
  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office
      \item Candidates must have at least one full semester of House membership as an Active Member
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item This process operates for one requirement at a time
  \item This process operates for one voting executive board position or the Chairperson at a time
  \item This process operates on the current election only
  \item Any requirements waived using this process are waived for all candidates for the given position for the current election process
\end{enumerate}
